### 2009-06-09 talk/icooolps2009-dotnet/paper.tex
don't show comments
try to incorporate some of the reviewers' comments

\begin{abstract}
The Common Language Infrastructure (CLI) is a virtual machine expressly
designed for implementing statically typed languages as C\#, therefore
programs written in dynamically typed languages are typically much slower than C\# when executed on .NET.

>>>>

\begin{abstract}
The Common Language Infrastructure (CLI) is a virtual machine expressly
designed for implementing statically typed languages such as C\#, therefore
programs written in dynamically typed languages are typically much slower than C\# when executed on .NET.
